Through the eyes of the teacher

### 2021-02-25 paper_1/paper_1_supplement_new_table.Rmd
update item analysis

res1.self<-rcorr(as.matrix(self.p.wide[,-1]))

flattenCorrMatrix(res2$r, res2$P)

res2.self<-flattenCorrMatrix(res2$r, res2$P)

@@

res1.stud<-rcorr(as.matrix(stud.p.wide[,-1]))

flattenCorrMatrix(res1.stud$r, res1.stud$P)

res2.stud<-flattenCorrMatrix(res1.stud$r, res1.stud$P)

@@

# Insignificant correlation are crossed
corrplot(res1.stud$r, type="upper", order="hclust",
         p.mat = res1.stud$P, sig.level = 0.01, insig = "blank")
# Insignificant correlations are leaved blank
corrplot(res1.stud$r, type="upper", order="hclust",
         p.mat = res1.stud$P, sig.level = 0.01, insig = "blank")
###############################################

>>>>

res1.self<-cor(self.p.wide[,-1])

rm(res1.self)
flattenCorrMatrix(res1.self$r, res1.self$P)

res1.self<-flattenCorrMatrix(res1.self$r, res1.self$P)

res2 <- rcorr(as.matrix(res1.self))
res2

@@

res1.stud<-cor(stud.p.wide[,-1])

# res1.stud<-rcorr(as.matrix(stud.p.wide[,-1]))
# 
# flattenCorrMatrix(res1.stud$r, res1.stud$P)
# 
# res2.stud<-flattenCorrMatrix(res1.stud$r, res1.stud$P)

@@

# # Insignificant correlation are crossed
# corrplot(res1.stud$r, type="upper", order="hclust",
#          p.mat = res1.stud$P, sig.level = 0.01, insig = "blank")
# # Insignificant correlations are leaved blank
# corrplot(res1.stud$r, type="upper", order="hclust",
#          p.mat = res1.stud$P, sig.level = 0.01, insig = "blank")
# ###############################################
